### 2014-10-09 LaTeX/RhodiumEmp.tex
more ugh

Our theoretical framework centers around the argument that variation in macroeconomic growth amongst countries in the midst of civil war can be explained by the spatial proximity between civil conflicts and urban centers. In constructing our dataset, we thus restrict our unit of observation to conflict-country years. This enables us to directly explore whether variation in growth amongst countries experiencing internal conflict can be explained by the proximity of conflict to cities. 
To measure macroeconomic performance, we focus on annual percent change in GDP from the World Development Indicators. We adopt this parameterization of our dependent variable because we expect that conflicts proximate to urban centers will generate abrupt changes in macroeconomic growth. Much of the extant literature linking internal armed conflict and economic growth has approached this instead using five or ten year averages of GDP growth. However, averaging over an arbitrary set of years may obfuscate meaningful variation in GDP growth over short temporal spans.

To determine the spatial proximity of conflict to urban centers, we collect information on the location of conflicts from the PRIO Conflict Site Dataset \citep{hallberg:2012}. This dataset contains information on the geographical centers of  armed conflict events and the area covered by each conflict at a yearly level from 1989 to 2008. To construct a time-series cross-sectional database of urban centers, we turn to yearly editions of The World Almanac from 1989 to 2008. Typically, the Almanacs list at least three major cities, including the capital, for each country and year from 1989 to 2008. To determine proximity, we calculate the great-circle distance in kilometers between the centroid of each of the conflicts with the centroids of city locations. Meaning that for each year we determine the distance between every conflict and every major city within a state.

@@

Our dependent variable is at the country-year and our key independent variable, distance between conflicts and major cities, is at the conflict-country-year level. To deal with this, we aggregate up to the country-year level by calculating the minimum logged distance any conflict is from a major city. Thus if a country faced, for example, four conflicts in one year, the datapoint that we would aggregate up to the country-year level would be for the conflict that was closest to a major city. This obviously is somewhat problematic as we end up discarding the information from the other conflicts. At the same time, we argue that this choice of aggregation is what conforms closest to our theoretical claims about economic activity only being severely disrupted in cases of conflicts being proximate to major cities. From the PRIO dataset we also bring in additional information about that conflict, specifically its intensity, the area of conflict, whether the conflict involves a territorial dispute, and its duration.

>>>>

\subsection{Measuring Spatial Proximity of Conflict to Urban Centers}

Our theoretical framework centers around the argument that variation in macroeconomic growth amongst countries in the midst of civil war can be explained by the spatial proximity between civil conflicts and urban centers. In constructing our dataset, we thus restrict the cases we include to only those country-years in which there was an internal armed conflict. Additionally, the unit of observation for this analysis is the country-year. This enables us to directly explore whether variation in growth amongst countries experiencing internal conflict can be explained by the proximity of conflict to cities.

To measure macroeconomic performance, we focus on annual percent change in GDP from the World Development Indicators. We adopt this parameterization of our dependent variable because we expect that conflicts proximate to urban centers will generate abrupt changes in macroeconomic growth. Much of the extant literature linking internal armed conflict and economic growth has approached this instead using five or ten year averages of GDP growth. However, averaging over an arbitrary set of years may obfuscate meaningful variation in GDP growth over short temporal spans.

We collect information on the location of conflicts from the PRIO Conflict Site Dataset \citep{hallberg:2012}. This dataset contains information on the geographical centers of armed conflict events and the area covered by each conflict at a yearly level from 1989 to 2008. In recent years, other geo-referenced datasets have been developed that go beyond just providing information on conflict centroids and area to providing an actual spatial grid structure through which to conduct analysis (e.g., \citealt{tollefsen:etal:2012}). For the purpose of this analysis, however, we deliberately avoid using these datasets since our primary interest is in examining variation in changes to GDP growth due to the proximity of conflict to urban centers.

% Note to Ben: Does that sound convincing? Probably not. The point that I'm trying to get across is that using the gridded data is not at the appropriate level of analysis. We need to say something here about this so if you can think of something better that'd be great.

To construct a time-series cross-sectional database of urban centers, we turn to yearly editions of The World Almanac from 1989 to 2008. More refined subnational data listing urban centers by their contribution to economic output would be the most direct way to test our hypothesis, however, cross-national data such as this over the time period of our analysis, especially for developing countries, is simply not available. The World Alamanac lists the major cities in a country by population, thus providing us with a second best approximation of the urban centers that are most relevant for a particular national economy. Typically, the Almanacs list at least three major cities, including the capital, for each country and year from 1989 to 2008. We use the top five major cities listed for each country and then determine their geographical centers.

% Again if you could add anything to why The World Alamanac data is the right choice that would be great.

Using our geo-referenced conflict and urban center data, we proceed to compute the proximity of every civil armed conflict in a country-year from every urban center listed in that year.\footnote{Distances between centroid locations were computed using an iterative method of distance calculation proposed by \citet{vincenty:1975}.} Since our unit of analysis is the country-year, we aggregate the distance between conflicts and major cities by calculating the  minimum logged distance any conflict is from a major city. For example, if a country faces, four conflicts in a year, the datapoint for that country-year level would be the minimum distance any conflict centroid is from any city centroid. This choice of aggregation is what conforms closest to our theoretical claims about macroeconomic activity only being severely disrupted in cases of conflicts being proximate to major cities.

@@

\subsection{Control Variables}

From the PRIO dataset we also bring in additional information about that conflict, specifically its intensity, the area of conflict, whether the conflict involves a territorial dispute, and its duration.
